---
title: "Perplexed_Pythons_Visualization_1"
author: "Timothy Nessel"
date: "12/1/2018"
output: html_document
---
I will start by loading the required packages if required
```{r}
if (!require("tidyverse")) install.packages("tidyverse")
if (!require("ggplot2")) install.packages("ggplot2")
if (!require("reshape2")) install.packages("reshape2")
if (!require("tidyr")) install.packages("tidyr")
if (!require("plyr")) install.packages("plyr")
library(tidyverse)
library(ggplot2)
library(reshape2)
library(tidyr)
library(plyr)
library(scales)
```
I will then read in the files to plot
```{r}
NAM_traits_signifiant_hits <- read.table("../data/NAM_traits_signifiant_hits.csv", header = TRUE, sep = ",")
NAM_effect_size <- read.table("../data/effect_size_maf.csv", header = TRUE, sep = ",")
```


To visualize the proportion of SNP_ID enrichment for each phenotypic trait, we will create a barplot in ggplot. 

We have to manipulate the y axis counts in order to get a proportion (cite https://stackoverflow.com/questions/36604127/creating-a-bar-plot-with-proportions-on-ggplot)

We also have to rotate the x axis for readability (cite https://stackoverflow.com/questions/1330989/rotating-and-spacing-axis-labels-in-ggplot2)

```{r}
q <- ggplot(NAM_traits_signifiant_hits, aes(trait)) +
  geom_bar(aes(y=..count../sum(..count..))) +
  scale_y_continuous(labels=percent_format())  #For proportion count y axis
q + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Proportion Variance Explained Replication") +
  xlab("Trait") +
  ylab("Proportion Variance Explained") # for the main and axis titles and For tilted x axis 
```

To visualize allele frequency vs effect size, we'll make a scatterplot with ggplot; with Minor Allele Frequency plotted along the x axis and effect size plotted along the y axis. We can use geom_smooth to creat a fitted line, and also use transparency to show overlap.
```{r}
ggplot(data = NAM_effect_size, mapping = aes(x=maf, y=effect_size_abs)) +
  geom_point(alpha=0.4) + 
  geom_smooth() + 
  ggtitle("Minor allele frequency vs effect size: Replication") +
    xlab("Minor Allele Frequency") +
    ylab("Effect Size") #gives main title and axis labels
  
```


